This is the user manual for the new \textit{LandPortal}, it has been structured as a set of questions and answers.

\subsection{How do I start a new debate?}
To start a new debate, you must load the debates view in the path \textit{/debate/debates}.  If you are logged into the new \textit{LandPortal} you will see a blue button to create a new debate in the right side.

After clicking that button the form to create a new debate will load.  You must fill the form (the fields marked with an asterisk are required and can not be left empty) and click the \textit{save} button.  After clicking the \textit{save} button (and if the form was correctly filled) the system will create the new debate.

By default all new debates are created with a ``\textit{coming soon}'' status, which means that the comments are closed until the debate's period starts.  When an administrator changes the debate status to ``\textit{open}'' and opens the comments, the users will be able to post new comments and participate into the debate.

\subsection{How do I close a debate?}
This action is restricted to users with administration privileges.

To close an open debate you must load the detailed view of the debate that you want to close.  In the bottom left you will see a blue button to edit the debate.

After clicking that button, the system will load a form (similar to the debate creation form) in which you can choose the correct settings for the debate. In the form, change the status of the debate to ``\textit{closed}'' and close the comments.  Click the \textit{save} button to save the changes.

After a debate has been closed, the users can see the existing comments, but can not create new ones.

\subsection{How can I register into the portal?}
To create a new account into the new \textit{LandPortal} you must load the home view and click the ``\textit{sign in}'' button in the upper right corner.  Once in the \textit{sign in} view you can choose between a tab to log into the system with an existing account, or to create a new account.

Choose the tab to create a new account and you will see the register form.  To create your account fill the form (the required fields are marked with an asterisk and can not be left empty) and click the button ``\textit{register}''.

\textbf{WARNING}  Your new account will not be usable right after the registration, For security reasons an administrator has to activate your account before you can log into the system.

\subsection{How can I moderate new registrations?}
This action is restricted to users with administration privileges.

By default, the new user registrations are in a ``\textins{disabled}'' state, which means that the user can not log into the system.  To enable the new user accounts, the admin must load the ``\textit{people}'' tab in the administration view.  The \textit{people} view shows a list of all user accounts (disabled or not) existing into the system.  To activate the user accounts, the administrator has to select the users and click the \textit{update} button.

\subsection{How can I moderate articles?}
This action is restricted to users with administration privileges.

The administrator can edit or delete any \textit{article}\footnote{In this context, \textit{articles} refers to any content in the social section of the LandPortal, such as news, events, debates, etc.}.  To delete a certain \textit{article} you must load its detailed view and click the button \textit{edit} or \textit{delete}.

The administrator can also edit or delete any user comments.  To do this, you must click the button \textit{edit} or \textit{delete} that appears under every comment.