En la tabla \ref{table:reportes_aceptacion} se muestran los reportes obtenidos de
los usuarios durante las pruebas de aceptación.  Cada entrada en la tabla contará
con los siguientes campos:
\begin{description}
	\item[Descripción] Descripción del reporte realizada por el usuario.  Es importante
		destacar que la descripción se incluirá tal y como se recibió por parte
		del usuario y, por tanto, se encontrará en inglés.
	\item[Estado] Estado del reporte.  Indica si el reporte ha sido aceptado como
		un error en el sistema o no.
	\item[Respuesta]  Respuesta tomada ante el reporte.
\end{description}

Todos los reportes que figuran en la tabla se han podido reproducir correctamente.
Aquellos reportes aceptados han sido solucionados antes de la entrega de la versión
final del sistema.

\begin{longtable}[c]{|p{60mm}|p{20mm}|p{50mm}|}
	\caption{Reportes tras las pruebas de aceptación\label{table:reportes_aceptacion}}\\
		%Cabecera en la primera pagina
		\hline
		\multicolumn{3}{|c|}{\textbf{Reportes tras las pruebas de aceptación}}\\
		\hline
		\textbf{Descripción} & \textbf{Estado} & \textbf{Respuesta}\\
		\hline
		\hline
	\endfirsthead

		%Cabecera en el resto de páginas
		\hline
		\multicolumn{3}{|c|}{\textbf{Continuación de la tabla \ref{table:reportes_aceptacion}}}\\
		\hline
		\textbf{Descripción} & \textbf{Estado} & \textbf{Respuesta}\\
		\hline
		\hline
	\endhead

	\hline
	\endfoot

	Community page is entirely empty, normal? & Rechazado & La página estaba vacía porque aún no se había insertado ninguna organización en el sistema\\
	\hline
	Data sources menu has some issues: twice the same sources is cited (one with the right name one with a type: Faostat: Statistcis division of the FAO) & & \\
	\hline
	The data sources menu is using multiple time the same value, creating issues with the second menu (not pointing to the right optgroup) & & \\
	\hline
	It seems that all countries are in spanish in the map & Aceptado & Resuelto \\
	\hline
	Label issues: in the data sources one cannot read the full name, in e.g. \url{http://5.9.221.11/book/countries/GNQ?indicator=INDFAOSTAT6&comparing-country=ABW} and the button in blue has a similar problem & Aceptado & Resuelto\\
	\hline
	The widget by country in the center below the social economic indicators has also some label issues, like when you go to DRC, only half of the country name display & Aceptado & Resuelto \\
	\hline
	In country main index ranking at the left column, the label seems wrong too, using a code rather than a name? & Aceptado & Resuelto\\
	\hline
	In the widget, the selection of countries is strange: there are white lines in the middle of the list, plus countries that are not sorted alphabetically as usual & Aceptado & Resuelto \\
	\hline
	In indicators (\url{http://5.9.221.11/book/indicators}) expanding all reveal some strange things like the ``temporal topics'' & Aceptado & Resuelto \\
	\hline
	Most of the links in \url{http://5.9.221.11/book/reuse} are broken & Aceptado & Resuelto \\
	\hline
	On the blog.  Before going live it would be good to ensure that postings come from a real named person, rather than ``admin'' & Aceptado & Resuelto \\
	\hline
	It would be great if land debates display ``Fascilited by'' with a real name, rather than username & Aceptado & Resuelto \\
	\hline
	On the list of debates consider placing ``Coming Soon'' debates either in a distinct box, or underneath ``Open'' debates & & \\
	\hline
	When I completed registration I got redirected to the homepage with no ``Registration complete'' messages & & \\
	\hline
	The auto-complete tagging for Regions and Countries doesn't feel quite right: a select list / multi-select component might work better here & & \\
	\hline
	The header with the logo on the left and the three entries is not consistent. On the homepage, there is no indication this is the home page and ``landLibrary'' is selected. Selecting an entry cite this entry next to the logo and then shift the header to the right. A ``home'' entry should be added and selected by default, this way there would always be something next to the logo & Rechazado & La entrada de ``LandLibrary'' está desactivada debido a que su renovación no forma parte de éste proyecto.  El enlace a ``home'' se encuentra en el propio logo de LandPortal\\
	\hline
	On \url{http://5.9.221.11/book/regions?region=1&indicator=INDOECD11&comparing-region=2} the ``JSON'', ``XML'', and ``CSV'' buttons all point to a ``data'' URI. This works in a browser but it's harder to download in a script (IMHO). I would have prefered having a distinct URI that points to the data with content negociated formats & Rechazado & Este tipo de negociación de contenido es soportado por el API, las visualizaciones utilizan un framework interno no orientado al usuario final. \\
	\hline
	Speaking about content negociation I found no trace of RDF/LOD on this page. Also, why only ``JSON'', ``XML'', and ``CSV'' buttons and no ``RDF'' button ? & Rechazado & Fuera del alcance del proyecto.  Requeriría crear consultas SPARQL para cada una de las diferentes visualizaciones ofrecidas \\
	\hline
	In ``Data Reuse'' there is a SPARQL interface that does not work yet but also does not explain to the user what he is currently seeing & Aceptado & Resuelto \\
	\hline
	The layout of \url{http://5.9.221.11/debate/events} is messed up on my screen and the calendar get pushed to the bottom right & Aceptado & Resuelto \\
	\hline
	User profile: there is no space to add any information on topics of interest, who you work for etc & & \\
	\hline
	Since debates are at the core for this page, it should be more prominent - currently there is blog, news, events first, then debates. The Debates tab should be the first one in the list, and the page seen when one opens this section of the LP & & \\
	\hline
	Data sources box is confusing: there are a number of sources though it isn't possible to read them in full as the titles are longer than the box), then indicators grouped by population indicators etc. The data sources box should only contain data sources, the indicators box the indicators grouped by sub-theme & & \\
	\hline
	The second reference in the data sources list for FAO statistics has a typo in ``statistics'' & & \\
	\hline
	There is a typo in the first indicator here, it should be women's access to land (currently woman access) & & \\
	\hline
	I also saw on the left hand side where the SIGI indicators appear that there is a repetition in the list & &\\
	\hline
	\hline
\end{longtable}
